---
title: "NBA_WEB"
---

title: "NBA Player Performance Analysis"
author: "Sneha Agrawal"


# Main Objective

Explore if playoff participation impacts player performance (GmSc)

Examine whether total rebounds relate to points scored (PTS)


# Audience

NBA Coaches & Analysts

Fantasy Basketball Players

Sports Fans & Stat Enthusiasts


#Initial EDA – Boxplot

Game Score (GmSc) by Playoff Participation

```{r}
library(readr)
library(ggplot2)


nba_data <- read_csv("C:/Statistics/nba.csv")


ggplot(nba_data, aes(x = factor(Playoffs), y = GmSc, fill = factor(Playoffs))) +
  geom_boxplot() +
  labs(title = "Game Score (GmSc) Distribution by Playoff Status",
       x = "Playoff Participation (0 = No, 1 = Yes)",
       y = "Game Score (GmSc)") +
  theme_minimal()

```

# Playoff players show higher and more varied Game Scores.




##Scatter Plot – Rebounds vs Points

Correlation Between Total Rebounds (TRB) and Points Scored (PTS)

```{r}

ggplot(nba_data, aes(x = TRB, y = PTS)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", col = "blue") +
  labs(title = "Correlation Between Total Rebounds and Points Scored",
       x = "Total Rebounds (TRB)",
       y = "Points Scored (PTS)") +
  theme_minimal()

```
#Weak but statistically significant correlation (r ≈ 0.091, p = 0.000161)

#Hypothesis Test: GmSc

H₀: No difference in GmSc between playoff and non-playoff playersH₁: There is a significant difference

p-value < 0.05 → Reject H₀

✅ Playoff participation correlates with higher performance


#Interpretation – Correlation

Pearson r = 0.091 → weak positive correlation

p = 0.000161 → statistically significant

Players with more rebounds tend to score slightly more points

#Conclusions

Playoff players have higher Game Scores

Rebounding has a weak but significant impact on scoring

Actionable Insight: Prioritize playoff experience and multi-metric evaluation



